Epidemic Tracking and Forecasting: Lessons Learned from a Tumultuous Year

### 2021-11-30 perspective/paper.tex
Compress refs

\usepackage[numbers]{natbib}
\usepackage{amssymb,amsmath,amsthm,bbm}

@@

Not unrelatedly, the last decade has also seen a rise in the importance of
\emph{digital surveillance} streams in public health, with improving epidemic
tracking and forecasting models being a key application of these data.  Digital
streams, such as search and social media trends, have constituted a large part
of the focus \citep{Ginsberg:2009, Brownstein:2009, Salathe:2012,
Kass-Hout:2013, Santillana:2015, Paul:2017}; however, even more broadly, data
from \emph{auxiliary} streams that operate outside of traditional public health
reporting, such as online surveys, medical devices, or electronic medical
records, have received considerable attention as well \citep{Kass-Hout:2011,
Carlson:2013, Viboud:2014, Smolinski:2015, Santillana:2016, Charu:2017,
Koppeschaar:2017, Yang:2019, Leuba:2020, Radin:2020, Ackley:2020}.

The Carnegie Mellon Delphi group, which the two of us co-lead, has worked in
both of these emerging disciplines---epidemic forecasting, and building relevant
auxiliary signals to aid such forecasting models---since 2012.  In 2020, as the
pandemic broke out, we struggled like many other groups to find ways to
contribute to the national efforts to respond to the pandemic.  We ended up
shifting our focus to lie nearly entirely on the data end of the spectrum,
pursuing several different directions in order to build and make available to
the public a variety of new indicators that reflect real-time COVID-19 activity
in the U.S.  Three papers in this collection describe this work from three
different perspectives.  A fourth describes international work by some of our
collaborators that parallels our group's work on online surveys in the U.S.

@@

\newpage
\bibliographystyle{unsrt}
\bibliography{../common/covidcast}

>>>>

\usepackage[numbers, sort&compress]{natbib}
\usepackage{amssymb,amsmath,amsthm,bbm}

@@

Not unrelatedly, the last decade or so also seen a rise in the importance of 
\emph{digital surveillance} in public health, with improving epidemic
tracking and forecasting models being a key application of these data.  Digital
streams, such as search and social media trends, have constituted a large part
of the focus \citep{Ginsberg:2009, Brownstein:2009, Salathe:2012,
Kass-Hout:2013, Santillana:2015, Paul:2017}; however, even more broadly,
\emph{auxiliary surveillance} streams, which operate outside of traditional
public health reporting, such as online surveys, medical devices, or electronic
medical records, have received considerable attention as well  
\citep{Kass-Hout:2011, Carlson:2013, Viboud:2014, Smolinski:2015,
  Santillana:2016, Charu:2017, Koppeschaar:2017, Yang:2019, Leuba:2020,
  Radin:2020, Ackley:2020}.

The Carnegie Mellon Delphi group, which the two of us co-lead, has worked in
both of these emerging disciplines---epidemic forecasting, and building relevant
auxiliary signals to aid such forecasting models---since 2012.  In 2020, as the
pandemic broke out, we struggled like many other groups to find ways to
contribute to the national efforts to respond to the pandemic.  We ended up
shifting our focus to lie nearly entirely on the data end of the spectrum,
pursuing several different directions in order to build and make available to
the public a variety of new indicators that reflect real-time COVID-19 activity
in the U.S.  Three papers in this collection describe this work from three
different perspectives.  A fourth describes international work by some of our
collaborators that parallels our group's work on surveys in the U.S.

@@

\bibliographystyle{unsrt}
\bibliography{../common/covidcast}
